---
title: "Wed_Inclass"
author: "Logan DeHay"
date: "11/17/2021"
output:
  pdf_document: default
  html_document: default
---

# This is a quick-turn challenge.  It relates to Question 2 of Quiz 8 in our course. Take a look at that quiz question and then.

## The researchers wanted to know if the spiders could run faster, on average, without the hindrance of a pedipalp

### Finish this writeUp and knit the result to a pdf file.  


### Then add this to your github account and turn it in by emailing me the link to it in your github account,



```{r, message=FALSE}
require(tidyverse)
require(tigerstats)
require(abd)
data("SpiderSpeed")
```
# Graphical Results
```{r, eval=TRUE}
#mydata <- gather(SpiderSpeed, variable, value) 
dat <- gather(SpiderSpeed, BorA, speed)
```

```{r}
boxplot(speed~BorA,data=dat, main="Speeds Before and After")
```
  
The boxplot illustrates a general trend of an increased pace in spiders after they have had one pedipalp removed. However, the speed after this procedure seems to have a greater variation.
  
# Numerical Results
  
```{r}
favstats(speed~BorA,data=dat)
```
  
The data calculations show an increased mean speed after the removal procedure, changing from 2.66 to 3.85.There also was an increased standard deviation from 0.64 to 0.99 speed variation.
  
# Inferential Results
  
```{r}
t.test(speed~BorA,data=dat)
```
  
The Welch Two sample T-Test indicated a p-value of 0.0004611 in which the spiders have a relatively small likelihood of mimicking this behavior without the alteration of the pedipalps. This p-value is small enough to indicate a correlation between the removal of a pedipalp and the speed of the spider. The 95% confidence interval ranges from 0.577 to 1.79.
  
  